---
title: "photodraw_analysis_R"
author: "Justin Yang"
date: "7/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(lmerTest)
library(tidyverse)
library(reshape2)
library(dplyr)
library(Hmisc)
library(ggthemes)
library(tidyboot)
library(wesanderson)
library(ggpubr)
library(psycho)
library(car)
```

## Load in data 

```{r setup}
analysis_dir <- getwd()
setwd('..')
photodraw_dir <- getwd()
feature_dir <- file.path(photodraw_dir, 'features')
results_dir <- file.path(photodraw_dir, 'results')
csv_dir <- file.path(results_dir, 'csv')

stroke_data <- read.csv(file.path(csv_dir,'photodraw2x2_stroke_data.csv'))
sketch_data <- read.csv(file.path(csv_dir,'photodraw2x2_sketch_data.csv'))
survey_data <- read.csv(file.path(csv_dir,'photodraw2x2_survey_data.csv'))
skeches_fc6 <- file.path(feature_dir, 'FEATURES_FC6_photodraw2x2_sketch.npy')
skeches_ins <- file.path(feature_dir, 'photodraw2x2_instance_features.npy')

sketch_data <- transform(sketch_data, isOutlier = as.logical(isOutlier))
sketch_data <- transform(sketch_data, activeSketchTime = activeSketchTime / 1000) # ms -> s
sketch_data <- filter(sketch_data, isOutlier==FALSE)

#names(sketch_data)
#str(sketch_data)
```


```{r}
names(sketch_data)
```

# Effect of various predictors on category-level evidence
## Nested model comparison: find which variables are important in predicting category-level evidence
```{r}
model10 <- lmer(prob_true_predict_fc6_logodds ~ condition * goal * isTypical + subjectiveSkill + numStrokes + totalInk + activeSketchTime  + (1 | gameID)+ ( 1 | category ), sketch_data)
model9 <- lmer(prob_true_predict_fc6_logodds ~ condition * goal + subjectiveSkill + numStrokes + totalInk + activeSketchTime + isTypical + (1 | gameID)+ ( 1 | category ), sketch_data)
model8 <- lmer(prob_true_predict_fc6_logodds ~ condition * goal + subjectiveSkill + numStrokes + totalInk + activeSketchTime + (1 | gameID)+ ( 1 | category ), sketch_data)
model7 <- lmer(prob_true_predict_fc6_logodds ~ condition * goal + subjectiveSkill + numStrokes + totalInk + (1 | gameID)+ ( 1 | category ), sketch_data)
model6 <- lmer(prob_true_predict_fc6_logodds ~ condition * goal + subjectiveSkill + numStrokes + (1 | gameID)+ ( 1 | category ), sketch_data)
model5 <- lmer(prob_true_predict_fc6_logodds ~ condition * goal + subjectiveSkill + (1 | gameID)+ ( 1 | category ), sketch_data)
model4 <- lmer(prob_true_predict_fc6_logodds ~ condition * goal + (1 | gameID)+ ( 1 | category ), sketch_data)
model3 <- lmer(prob_true_predict_fc6_logodds ~ condition + goal + (1 | gameID)+ ( 1 | category ), sketch_data)
model2 <- lmer(prob_true_predict_fc6_logodds ~ condition + ( 1 | gameID ) + ( 1 | category ), sketch_data)
model1 <- lmer(prob_true_predict_fc6_logodds ~ ( 1 | gameID ) + ( 1 | category ), sketch_data)

anova(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)
```

## Optimal model: prob_true_predict_fc6_logodds ~ condition * goal + subjectiveSkill + (1 | gameID) + (1 | category)
```{r}
# optimal model for use in paper. For classification accuracy, use: as.numeric(true_predict_fc6)
model5_acc <- lmer(prob_true_predict_fc6_logodds ~ condition * goal + subjectiveSkill + (1 | gameID)+ ( 1 | category ), sketch_data)
summary(model5_acc)
```


# Effect of various predictors on basic behavior
## Nested model comparison
```{r}
# exchange between numStrokes, totalInk, activeSketchTime , -- should we add "cat_typicality"?
model7 <- lmer(numStrokes ~ condition * goal * isTypical + subjectiveSkill + prob_true_predict_fc6_logodds + (1 | gameID) + (1 | category), sketch_data)
model6 <- lmer(numStrokes ~ condition * goal + subjectiveSkill + prob_true_predict_fc6_logodds + (1 | gameID) + (1 | category), sketch_data)
model5 <- lmer(numStrokes ~ condition * goal + subjectiveSkill +                                 (1 | gameID) + (1 | category), sketch_data)
model4 <- lmer(numStrokes ~ condition * goal +                                                   (1 | gameID) + (1 | category), sketch_data)
model3 <- lmer(numStrokes ~ condition + goal +                                                   (1 | gameID) + (1 | category), sketch_data)
model2 <- lmer(numStrokes ~ condition +                                                          (1 | gameID) + (1 | category), sketch_data)
model1 <- lmer(numStrokes ~                                                                      (1 | gameID) + (1 | category), sketch_data)

anova(model1, model2, model3, model4, model5, model6, model7)
```

## Optimal model
```{r}
model.a <- lmer(numStrokes ~ condition + goal + isTypical + (1 | gameID) + (1 | category), sketch_data)
model.b <- lmer(totalInk ~ condition + goal + isTypical + (1 | gameID) + (1 | category), sketch_data)
model.c <- lmer(activeSketchTime ~ condition * goal + isTypical + (1 | gameID) + (1 | category), sketch_data)
summary(model.a)
```

# Effect of typicality (within photo-cue analyses) 

## Effect of typicality on category-level logodd prediction probabilities
### Nested model selection
```{r}
model8 <- lmer(prob_true_predict_fc6_logodds ~ goal * inst_typicality + subjectiveSkill + numStrokes + totalInk + activeSketchTime +              (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo')) 
model7 <- lmer(prob_true_predict_fc6_logodds ~ goal * inst_typicality + subjectiveSkill + numStrokes + totalInk +                                 (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo')) 
model6 <- lmer(prob_true_predict_fc6_logodds ~ goal * inst_typicality + subjectiveSkill + numStrokes +                                             (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo')) 
model5 <- lmer(prob_true_predict_fc6_logodds ~ goal * inst_typicality + subjectiveSkill +                                                         (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo')) 
model4 <- lmer(prob_true_predict_fc6_logodds ~ goal * inst_typicality +                                                                            (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo'))
model3 <- lmer(prob_true_predict_fc6_logodds ~ goal + inst_typicality +                                                                           (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo'))
model2 <- lmer(prob_true_predict_fc6_logodds ~ goal +                                                                                             (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo'))
model1 <- lmer(prob_true_predict_fc6_logodds ~                                                                                                    (1 | gameID) + (1 | category) + (1 | imageURL), filter(sketch_data, condition == 'photo'))

anova(model1, model2, model3, model4, model5, model6, model7, model8)
```

### Optimal model
```{r}
# prob_true_predict_fc6_logodds or as.numeric(true_predict_fc6)

model.a <-lmer(prob_true_predict_fc6_logodds ~ goal * inst_typicality + subjectiveSkill + (1 | gameID) + ( 1 | category ) + (1 | imageURL), filter(sketch_data, condition=='photo'))

# testing to see what the interaction term really means
model.b <-lmer(prob_true_predict_fc6_logodds ~ inst_typicality + subjectiveSkill + (1 | gameID) + ( 1 | category ) + (1 | imageURL), filter(sketch_data, condition=='photo' & goal=='instancedraw'))
model.c <-lmer(prob_true_predict_fc6_logodds ~ inst_typicality + subjectiveSkill + (1 | gameID) + ( 1 | category ) + (1 | imageURL), filter(sketch_data, condition=='photo' & goal=='categorydraw'))

summary(model.c)
car::Anova(model.a)
```

## Effect of typicality on low level features
### Nested model comparison
```{r}
# exchange between numStrokes, totalInk, activeSketchTime 
model6 <- lmer(activeSketchTime ~ goal * inst_typicality + subjectiveSkill + prob_true_predict_fc6_logodds + (1 | gameID)+ ( 1 | category ) + (1|imageURL), filter(sketch_data, condition=='photo')) 
model5 <- lmer(activeSketchTime ~ goal * inst_typicality + subjectiveSkill + (1 | gameID) + ( 1 | category ) + (1|imageURL), filter(sketch_data, condition=='photo')) 
model4 <- lmer(activeSketchTime ~ goal * inst_typicality + (1 | gameID) + ( 1 | category ) + (1|imageURL), filter(sketch_data, condition=='photo'))
model3 <- lmer(activeSketchTime ~ goal + inst_typicality + (1 | gameID) + ( 1 | category ) + (1|imageURL), filter(sketch_data, condition=='photo'))
model2 <- lmer(activeSketchTime ~ goal + (1 | gameID) + ( 1 | category ) + (1|imageURL), filter(sketch_data, condition=='photo'))
model1 <- lmer(activeSketchTime ~ ( 1 | gameID ) + ( 1 | category ) + (1|imageURL), filter(sketch_data, condition=='photo'))

anova(model1, model2, model3, model4, model5, model6)
```

### Optimal model
```{r}
model.a <-lmer(numStrokes ~ goal * inst_typicality + subjectiveSkill + (1 | gameID) + ( 1 | category ) + (1 | imageURL), filter(sketch_data, condition=='photo'))
model.b <-lmer(totalInk   ~ goal * inst_typicality + subjectiveSkill + (1 | gameID) + ( 1 | category ) + (1 | imageURL), filter(sketch_data, condition=='photo'))
model.c <-lmer(activeSketchTime ~ goal * inst_typicality + subjectiveSkill + (1 | gameID) + ( 1 | category ) + (1 | imageURL), filter(sketch_data, condition=='photo'))

summary(model.a)
car::Anova(model.a)

```


## Analyze variance data
```{r}
var_data <- read.csv(file.path(csv_dir,'photodraw2x2_category_by_experiment_variances.csv'))
model <- lmer(fc6_variance ~ condition * goal + (1 | category), var_data)
summary(model)
```

```{r}
model <- lm(fc6_variance ~ condition * goal, var_data)
summary(model)
```

# Visualizations
## Visualize num strokes

```{r get conf. intervals}
bstrap_activeSketchTime_photo <- c()
bstrap_activeSketchTime_text <- c()
bstrap_numStrokes_photo <- c()
bstrap_numStrokes_text <- c()
bstrap_totalInk_photo <- c()
bstrap_totalInk_text <- c()
filtered_data <- filter(sketch_data, isOutlier==FALSE)
filtered_photo <- subset(filtered_data, condition=="photo")
filtered_text <- subset(filtered_data, condition=="text")
for (i in 1:1000){
  bstrap_activeSketchTime_photo <- c(bstrap_activeSketchTime_photo, mean(sample(filtered_photo$activeSketchTime,100,replace=T)))
  bstrap_activeSketchTime_text <- c(bstrap_activeSketchTime_text, mean(sample(filtered_text$activeSketchTime,100,replace=T)))
  bstrap_numStrokes_photo <- c(bstrap_numStrokes_photo, mean(sample(filtered_photo$numStrokes,100,replace=T)))
  bstrap_numStrokes_text <- c(bstrap_numStrokes_text, mean(sample(filtered_text$numStrokes,100,replace=T)))
  bstrap_totalInk_photo <- c(bstrap_totalInk_photo, mean(sample(filtered_photo$totalInk,100,replace=T)))
  bstrap_totalInk_text <- c(bstrap_totalInk_text, mean(sample(filtered_text$totalInk,100,replace=T)))
}
#numStrokes:
print("The 95% CI for numStrokes is:")
print(paste("Photo:",quantile(bstrap_numStrokes_photo,.025)[[1]], ',' ,quantile(bstrap_numStrokes_photo,.975)[[1]]))
print(paste("Text:",quantile(bstrap_numStrokes_text,.025)[[1]], ',' ,quantile(bstrap_numStrokes_text,.975)[[1]]))
# totalInk:
print("The 95% CI for activeSketchTime is:")
print(paste("Photo:",quantile(bstrap_activeSketchTime_photo,.025)[[1]], ',' ,quantile(bstrap_activeSketchTime_photo,.975)[[1]]))
print(paste("Text:",quantile(bstrap_activeSketchTime_text,.025)[[1]], ',' ,quantile(bstrap_activeSketchTime_text,.975)[[1]]))
# activeSketchTime
print("The 95% CI for totalInk is:")
print(paste("Photo:",quantile(bstrap_totalInk_photo,.025)[[1]], ',' ,quantile(bstrap_totalInk_photo,.975)[[1]]))
print(paste("Text:",quantile(bstrap_totalInk_text,.025)[[1]], ',' ,quantile(bstrap_totalInk_text,.975)[[1]]))
```

```{r, fig.width=6,fig.height=4}
df = filter(sketch_data, isOutlier==FALSE)[c("goal","condition","numStrokes","prob_true_predict_fc6_logodds")] 
df2 = var_data[c("goal","condition","fc6_variance")] 

df.strokes <- df %>%
  group_by(goal, condition) %>%
  tidyboot_mean(numStrokes)
df.probs <- df %>%
  group_by(goal, condition) %>%
  tidyboot_mean(prob_true_predict_fc6_logodds)

df2.vars <- df2 %>%
  group_by(goal, condition) %>%
  tidyboot_mean(fc6_variance)
df.strokes$goal <- factor(df.strokes$goal, levels = c('instancedraw', 'categorydraw'))
df.probs$goal <- factor(df.probs$goal, levels = c('instancedraw', 'categorydraw'))
df2.vars$goal <- factor(df2.vars$goal, levels = c('instancedraw', 'categorydraw'))

p1 <- df.strokes %>% 
  ggplot(aes(x=condition, y=mean, fill=goal, alpha=condition)) + #, show.legend=F
  geom_bar(stat="identity", position = position_dodge(), width=0.9) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +  
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1, position = position_dodge(0.9)) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 15)) +
  labs(y="number of strokes") + 
  scale_alpha_ordinal(range = c(1, 0.5))

p2 <- df.probs %>% 
  ggplot(aes(x=condition, y=mean, fill=goal, alpha=condition)) + #, show.legend=F    
  geom_bar(stat="identity",position = position_dodge(0.9), width=0.9) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1, position = position_dodge(0.9)) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 5)) + 
  labs(y="logodds target probability") +
  scale_alpha_ordinal(range = c(1, 0.5))

p3 <- df2.vars %>% 
  ggplot(aes(x=condition, y=mean, fill=goal, alpha=condition)) +   # , show.legend=T
  geom_bar(stat="identity",position = position_dodge(0.9), width=0.9) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1, position = position_dodge(0.9)) +
  theme_few() + 
  coord_cartesian(ylim=c(500, 1000)) + #500
  labs(y="variance within category") + 
  scale_alpha_ordinal(range = c(1, 0.5))

ggarrange(p1, p2, p3, nrow = 1, common.legend = TRUE, legend="bottom", align = "v")

#ggsave('../results/plots/photodraw_2x2_strokes_clfprobs.pdf', height = 8, width = 10, units = 'cm', useDingbats = F)
```

```{r, fig.width=6,fig.height=4}
df = filter(sketch_data, isOutlier==FALSE)[c("goal","condition","cat_correct_mean","inst_correct_mean","cat_rt_mean","inst_rt_mean")] 

df.cat_accs <- df %>%
  group_by(goal, condition) %>%
  tidyboot_mean(cat_correct_mean)
df.inst_accs <- df %>%
  filter(condition == 'photo') %>%
  group_by(goal) %>%
  tidyboot_mean(inst_correct_mean)
df.cat_rts <- df %>%
  group_by(goal, condition) %>%
  tidyboot_mean(cat_rt_mean)
df.inst_rts <- df %>%
  filter(condition == 'photo') %>%
  group_by(goal) %>%
  tidyboot_mean(inst_rt_mean)

df.cat_accs$goal <- factor(df.cat_accs$goal, levels = c('instancedraw', 'categorydraw'))
df.inst_accs$goal <- factor(df.inst_accs$goal, levels = c('instancedraw', 'categorydraw'))
df.cat_rts$goal <- factor(df.cat_rts$goal, levels = c('instancedraw', 'categorydraw'))
df.inst_rts$goal <- factor(df.inst_rts$goal, levels = c('instancedraw', 'categorydraw'))

p1 <- df.cat_accs %>% 
  ggplot(aes(x=condition, y=mean, fill=goal, alpha=condition)) + #, show.legend=F
  geom_bar(stat="identity", position = position_dodge(), width=0.9) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +  
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1, position = position_dodge(0.9)) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 1)) +
  labs(y="category recognition accuracy") + 
  scale_alpha_ordinal(range = c(1, 0.5)) + 
  geom_hline(yintercept=1/32, linetype="dashed", color = "lightgrey", size = .9)

p2 <- df.inst_accs %>% 
  ggplot(aes(x=goal, y=mean, fill=goal)) + #, show.legend=F    
  geom_bar(stat="identity",position = position_dodge(0.9), width=0.9) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1, position = position_dodge(0.9)) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 1)) + 
  labs(x = "condition", y="instance recognition accuracy") +
  scale_x_discrete(labels=c("instance","category")) + 
  scale_alpha_ordinal(range = c(1, 0.5)) + 
  geom_hline(yintercept=1/8, linetype="dashed", color = "lightgrey", size=.9) 


p3 <- df.cat_rts %>% 
  ggplot(aes(x=condition, y=mean, fill=goal, alpha=condition)) +   # , show.legend=T
  geom_bar(stat="identity",position = position_dodge(0.9), width=0.9) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1, position = position_dodge(0.9)) +
  theme_few() + 
  coord_cartesian(ylim=c(1000, 8000)) + #500
  labs(y="category recognition time (ms)") + 
  scale_alpha_ordinal(range = c(1, 0.5))

p4 <- df.inst_rts %>% 
  ggplot(aes(x=goal, y=mean, fill=goal)) +   # , show.legend=T
  geom_bar(stat="identity",position = position_dodge(0.9), width=0.9) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1, position = position_dodge(0.9)) +
  theme_few() + 
  coord_cartesian(ylim=c(1000, 8000)) + #500
  labs(x="condition", y="instance recognition times (ms)") + 
  scale_x_discrete(labels=c("instance","category")) + 
  scale_alpha_ordinal(range = c(1, 0.5))

ggarrange(p1, p2, p3, p4, nrow = 1, common.legend = TRUE, legend="bottom", align = "v", widths = c(2, 1.5, 2, 1.5))
#ggsave('../results/plots/photodraw_2x2_recog_accs_rts.pdf', height = 8, width = 14, units = 'cm', useDingbats = F)


```


```{r}
library(car)

# is there an interaction between level of of abstraction and condition?
d = filter(sketch_data, isInvalid==FALSE & isOutlier==FALSE)[c("category", "condition", "cat_id","gameID", "prob_true_predict_fc6", "prob_true_predict_pixel")]

# melt fc6 and pixel recognizabilities into one column
d = melt(data = d, id.vars = c("gameID", "category", "condition", "cat_id"), measure.vars = c("prob_true_predict_pixel", "prob_true_predict_fc6"))
d <- na.omit(d)
model = lmer(value ~ condition + variable + condition:variable + (1 | category) + (1 | gameID) , data = d)
summary(model)
Anova(model)
anova(model)
```
```{r}
model = lmer(value ~ variable + (1 | cat_id) + (1 | gameID) , data = d)
summary(model)
#mean(filter(d, variable == 'prob_true_predict_fc6', condition == 'photo')[['value']])
```


```{r, fig.width=3,fig.height=4}
d.errbar <- d %>%
  group_by(variable) %>%
  tidyboot_mean(value)
d.errbar %>% 
  ggplot(aes(x=variable, y=mean, fill=variable)) +
  geom_bar(stat="identity", width=0.9, show.legend=F) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +  
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 1)) +
  scale_x_discrete(labels = c('pixel-level','fc6-level')) +
  labs(x="feature level",y="Probability estimate")
#, title="Sketch recognizability across feature level")
d

```

```{r, fig.width=6,fig.height=4}

df = filter(sketch_data, isInvalid==FALSE & isOutlier==FALSE)[c("condition","numStrokes", "totalInk", "activeSketchTime")] 

df.strokes <- df %>%
  group_by(condition) %>%
  tidyboot_mean(numStrokes)
df.ink <- df %>%
  group_by(condition) %>%
  tidyboot_mean(totalInk)
df.time <- df %>%
  group_by(condition) %>%
  tidyboot_mean(activeSketchTime)

p1 <- df.strokes %>% 
  ggplot(aes(x=condition, y=mean, fill=condition)) +
  geom_bar(stat="identity", width=0.9, show.legend=F) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +  
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 15)) +
  labs(y="number of strokes") 
p2 <- df.ink %>% 
  ggplot(aes(x=condition, y=mean, fill=condition)) +
  geom_bar(stat="identity", width=0.9, show.legend=F) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +  
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 1500)) +
  labs(y="total ink used") 
p3 <- df.time %>% 
  ggplot(aes(x=condition, y=mean, fill=condition)) +
  geom_bar(stat="identity", width=0.9, show.legend=F) + scale_fill_manual(values=rev(wes_palette(n=2, name="Royal1"))) +  
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width = 0, size = 1) +
  theme_few() + 
  coord_cartesian(ylim=c(0, 40000)) +
  labs(y="active sketch time") 

ggarrange(p1, p3, p2, ncol=3, nrow=1)

#ggsave('../results/plots/photodraw_strokes_clfprobs.pdf', height = 10, width = 8, units = 'cm', useDingbats = F)
```
